Kindly Bent to Free Us

### 2019-07-11 kindly/lang.tex
Remove the TODOs.
Minor cosmetics.

\subsubsection{Kind checking}

\TODO{Present this if we have enough space}

\subsubsection{Pattern matching}

\TODO{Present this if we have enough space}

\clearpage
\subsection{Semantics}
\label{sem}
\input{internal-grammar}

\lstMakeShortInline[style=rule]@

@@

The evaluation function is indexed by a step count so that each
invocation is guaranteed to terminate either with an error, a timeout,
or a meaningful result. Hence its return type is a monad
\lstinline/'a sem/ which combines error reporting, timeout, and a
result of type \lstinline/'a/:
\begin{lstlisting}
type 'a sem = Error of string | TimeOut | Ok of 'a
# eval : store -> perm -> venv -> int -> exp -> (store * perm * result) sem
\end{lstlisting}
It evaluates the given expression in the context of an initial store, a
permission to use addresses in the store, a value environment, and a
step count. If successful, it returns the final store, the remaining
permissions, and the actual result.

@@

The definition uses concrete OCaml syntax with some pretty
printing. The pervasive \lstinline/let*/ operator acts as monadic bind
for the \lstinline/sem/ monad. The function header of @eval@ checks
whether time is up and otherwise proceeds processing the expression.

>>>>

% \subsubsection{Kind checking}

% \TODO{Present this if we have enough space}

% \subsubsection{Pattern matching}

% \TODO{Present this if we have enough space}

% \clearpage
\subsection{Semantics}
\label{sem}
\input{internal-grammar}

\lstMakeShortInline[style=rule,columns=flexible,basicstyle=\normalsize\normalfont]@

@@

The evaluation function is indexed by a step count so that each
invocation is guaranteed to terminate either with an error, a timeout,
or a meaningful result. Hence its return type is a monad
\lstinline/'a sem/ which combines error reporting, timeout, and a
result of type \lstinline/'a/:
\begin{lstlisting}
type 'a sem = Error of string | TimeOut | Ok of 'a
val eval : store -> perm -> venv -> int -> exp -> (store * perm * result) sem
\end{lstlisting}
It evaluates the given expression in the context of an initial store, a
permission to use addresses in the store, a value environment, and a
step count. If successful, it returns the final store, the remaining
permissions, and the actual result.

@@

The definition uses concrete OCaml syntax with some pretty
printing. The pervasive @let*@ operator acts as monadic bind
for the \lstinline/sem/ monad. The function header of @eval@ checks
whether time is up and otherwise proceeds processing the expression.
